---
title: "Exam 3 RMarkdown"
font size: 11pt
geometry: margin=1in
linestretch: 2
author: "Cynthia Sun"
date: "7/8/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part One: Tidy Census Gini

```{r eval = FALSE}
#clear environment
rm(list = ls(all=TRUE))

# load tidycensus 
library(tidycensus)
census_api_key("0979f51018f9aad11498289530215de0e9dd4c4f", install = TRUE,
               overwrite = TRUE)

gini_2010 <- load_variables(year = 2010, "acs5")
gini_2015 <- load_variables(year = 2015, "acs5")

View(gini_2010)
View(gini_2015)

# filter gini inequality
gini_2010 <- get_acs(geography = "county", 
                 variables = c(gini = c("B19083_001")), 
                 year = 2010)
gini_2015 <- get_acs(geography = "county", 
                     variables = c(gini = c("B19083_001")), 
                     year = 2010)
# add years
gini_2010$year = 2010
gini_2015$year = 2015

# combine the datasets into a panel data
library(data.table)
library(dplyr)
inequality_panel = left_join(x = gini_2010,
                          y = gini_2015,
                          by = "NAME")

# rename NAME variable to `state`
setnames(inequality_panel, "NAME", "state")

# rename other variables too, make the irrelevant ones null
inequality_panel <- subset(inequality_panel, select = -c(variable.y))
inequality_panel <- subset(inequality_panel, select = -c(GEOID.y))
inequality_panel$year.x <- NULL
inequality_panel$year.y <- NULL

# rename variables to specify the year
setnames(inequality_panel, "moe.x", "moe 2010")
setnames(inequality_panel, "moe.y", "moe 2015")
setnames(inequality_panel, "variable.x", "variable")
setnames(inequality_panel, "estimate.x", "estimate 2010")
setnames(inequality_panel, "estimate.y", "estimate 2015")
setnames(inequality_panel, "GEOID.x", "GEOID")

#peek at head of data
head(inequality_panel)
```

Reshape to wide format.
```{r}
# reshape panel to wide format
library(tidyverse)
inequality_wide <-
  inequality_panel %>%
  pivot_wider(id_cols = c("state", "GEOID", "estimate 2010", "estimate 2015"),
              names_from = c("state", "GEOID"),
              values_from = c("estimate 2010", "estimate 2015"))
head(inequality_wide)
```
Reshape to long format.
```{r}
# reshape panel to long format
inequality_long <- # reshape panel to wide format
  inequality_wide %>%
  pivot_longer(cols = starts_with('estimate'),
               names_to = c("state", "GEOID"),
               names_sep = " ",
               values_to = c("estimate 2010", "estimate 2015"),
               values_drop_na = FALSE)

head(inequality_long)
```
## Part Two: WDI GDP

```{r}
library(WDI)
gdp_current = WDI(country = "all", indicator = "NY.GDP.MKTP.CD",
                    start = 2006, end = 2007, extra = FALSE, cache = NULL)

#deflate data with USD 2015
deflator_data = WDI(country = "all", indicator = "NY.GDP.DEFL.ZS",
                    start = 2006, end = 2007, extra = FALSE, cache = NULL)

# rename deflator variable
library(data.table)
setnames(deflator_data, "NY.GDP.DEFL.ZS", "deflator")

#subset to get data frame with only USD, remove deflator table
usd_deflator <- subset(deflator_data, country == "United States")
rm(deflator_data)

#drop unnecessary variables
usd_deflator$iso2c <- NULL
usd_deflator$country <- NULL

#merge to match years + deflation rates by USD
gdp_deflated = left_join(x = gdp_current,
                          y = usd_deflator,
                          by = "year")
setnames(gdp_deflated, "NY.GDP.MKTP.CD", "GDP")

# ACTUALLY FUNCTION OF DEFLATING IT
gdp_deflated$deflated_amount = gdp_deflated$GDP/
  (gdp_deflated$deflator/100)

# peek at data
head(gdp_deflated)
```
- I picked constant 2015 USD because it is more accurate.

### Question 10
The three main components are: The User Interface, the Server and the shinyApp(ui, server) functions. The User Interface consists of Input ID and Output ID. The Server also consists of the Input ID and Output ID.

## PART THREE: USAID
```{r}
## READ PDF FROM WEBSITE
# first check libraries
library(pdftools)
library(tidyr) 
library(tidytext) 
library(dplyr) 
library(stringr) 
library(ggplot2)

# read pdf from the website
armeniatext =pdf_text(pdf =
                  "https://pdf.usaid.gov/pdf_docs/PA00TNMG.pdf")

# convert to df
armeniatext <- as.data.frame(armeniatext, stringAsFactors = FALSE) 
armeniatext$page=c(1:65) 
colnames(armeniatext)[which(names(armeniatext) == "armeniatext")] <- "text"

# TOKENIZE NOW
tidy_armenia <- armeniatext %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

# Frequency
armeniafreq <- tidy_armenia %>%
  count(word, sort = TRUE)
head(armeniafreq, n = 5)

```
### Github Repo
[Cynthia Sun's Github Repo](https://github.com/cynthiamsun/DataSciExam3)